Sketch Recognition and Understanding

### 2009-04-27 trunk/draft/SketchMaster.tex
return to old but adding supervisor to first page

% During the editing process you will not want to view and print the
% whole document. Uncomment the command below so that only the
% chapters that you want to work on are visible.
%\includeonly{ChapterIntroduction}
%\documentstyle[11pt,unhthesis]{report}
\documentclass[11pt,doublespace]{report}%{Sketchthesis}

@@

\begin{document}
                                                        % TITLE PAGE
                                                        %======================
          % My theses title  using Particle Swarm Optimization Algorithm
%\author{Maha Mohammed Nabeel El Meseery}                               % Y name
%\prevdegrees{B.S.,Computer  Engineering}       		% Your old degree
%\major{Computer Engineering}                            % My current major
%\degree{Master of Science}                              % My new degree
%\degreemonth{}                                      % When awarded. to be added when known
%\degreeyear{}                                      %
%%th today or first day of writing  December 26 2005 
%%\thesisdate[]                                     % Date of document.
%\DOCUMENTtype{Thesis}                                   % or DISSERTATION
%\Documenttype{Thesis}                                   % or Dissertation
%\documenttype{Thesis}

   \vspace*{0.375in}
               {\Large\bf\title{Sketch Recognition and Understanding}  }
                                 \vspace*{0.375in}

                                \vspace*{\fill}\par
                                      BY
                                \vspace*{\fill}\par
                               {\Large \author{Maha Mohammed Nabeel El Meseery }}
                                     \par
                               B.Sc.,Computer  Engineering
                                \vspace*{\fill}\par
                                    Thesis
                                \vspace*{\fill}\par
                           Submitted to the Faculty of Engineering Cairo University\\
                         in partial fulfillment of \\
                   the requirements for the degree\ of
                                \vspace*{\fill}\par
                                   Master of Science
                                     \par
                                      in
                                     \par
                                   Master of Science
                                \vspace*{\fill}\par

                                                        % or dissertation
\maketitle

\providecommand{\tabularnewline}{\\}
                                                        % COPYRIGHT PAGE
                                                        %======================
%\copyrightyear{2009}                                    % Delete these
%\makecopyright                                          % if no copyright
                                                    % APPROVAL                                                         %======================
%\thispagestyle{empty}               % Don't do headers or footers.
%\newpage                                                             
%\begin{center}     
%\LARGE  
%\textbf{Sketch Recognition using Particle Swarm Optimization Algorithm}\\
%\normalsize by      \\ 
%\Large  \textbf{ Maha mohamed Nabeel El Meseery}\\
%\vspace*{0.4in}        
%\normalsize
%A Thesis Submitted To the\\
%Faculty of Engineering, Cairo University\\
%in Partial Fulfillment of the\\
%Requirements for the Degree of\\
%MASTER OF SCIENCE
%in\\
%COMPUTER ENGINEERING\\
%
%\end{center}
%          
%    Approved by\\                                           
%Examining Committee:\\
% \makebox[6in]{\hrulefill}\\ 
%Professor Nevin Darwish, Thesis Main Advisor\\
% \makebox[6in]{\hrulefill}\\ 
%Professor Samia Mashali,Thesis Advisor \\
% \makebox[6in]{\hrulefill}\\  
%Assoc. Professor Magda Fayek,Thesis Advisor\\ 
% \makebox[6in]{\hrulefill}\\ 
%Professor  Ashraf Abd El Wahab, Member\\
% \makebox[6in]{\hrulefill}\\ 
%Professor Mohamed Zaki Abd ElMegeed, Member\\
% \makebox[6in]{\hrulefill}\\ 
  % \\   you need...\\
%\makeapproval                                           %

@@

                                                        % ACK. PAGE
                                                        %======================
 \def\acknowledgments
   {\vspace*{0.5in}
    \thispagestyle{plain}
    \chapter*{Acknowledgments}
    \addcontentsline{toc}{section}{Acknowledgments}

   }

\def\endacknowledgments{\par}

\begin{acknowledgments}     
                            % Delete these if
All praise is due to Allah Who guided me to this. I could not truly have been led aright if Allah had not guided me.

@@

%------------------------------------------------------------------------------
%  Document body - Place text into individual include files, such as
%                  as "chap1.tex", or replace each "\include{}" statement
%                  with your actual document text.
%------------------------------------------------------------------------------
\begin{abstract}          
% ABSTRACT PAGE
%==============================
% Creates the abstract page.
%   Your text goes here. Just
%   follow the rules given in
%   the LaTeX manual on how to
%   enter/format text using
%   LaTeX commands.

@@

\end{abstract}                              % This ends the page.

>>>>

% During the editing process you will not want to view and print the
% whole document. Uncomment the command below so that only the
% chapters that you want to work on are visible.
%\includeonly{ChapterIntroduction}
%\documentstyle[11pt,unhthesis]{report}
\documentclass[11pt,doublespace]{Sketchthesis}

@@

\begin{document}
                                                        % TITLE PAGE
                                                        %======================
\title{Sketch Recognition and Understanding}             % My theses title  using Particle Swarm Optimization Algorithm
\author{Maha Mohammed Nabeel El Meseery}                               % Y name
\prevdegrees{B.S.,Computer  Engineering}       		% Your old degree
\major{Computer Engineering}                            % My current major
\degree{Master of Science}                              % My new degree
\degreemonth{}                                      % When awarded. to be added when known
\degreeyear{}                                      %
\superad{Professor Nevin Darwish\\Professor Samia Mashali\\Assoc. Professor Magda Fayek\\}
%th today or first day of writing  December 26 2005 
%\thesisdate[]                                     % Date of document.
\DOCUMENTtype{Thesis}                                   % or DISSERTATION
\Documenttype{Thesis}                                   % or Dissertation
\documenttype{Thesis}                                   % or dissertation

\maketitle

                                                        % COPYRIGHT PAGE
                                                        %======================
%\copyrightyear{2009}                                    % Delete these
%\makecopyright                                          % if no copyright
                                                    % APPROVAL                                                         %======================
%\thispagestyle{empty}               % Don't do headers or footers.
%\newpage                                                             
%\begin{center}     
%\LARGE  
%\textbf{Sketch Recognition using Particle Swarm Optimization Algorithm}\\
%\normalsize by      \\ 
%\Large  \textbf{ Maha mohamed Nabeel El Meseery}\\
%\vspace*{0.4in}        
%\normalsize
%A Thesis Submitted To the\\
%Faculty of Engineering, Cairo University\\
%in Partial Fulfillment of the\\
%Requirements for the Degree of\\
%MASTER OF SCIENCE
%in\\
%COMPUTER ENGINEERING\\
%
%\end{center}
%          
%    Approved by\\                                           
%Examining Committee:\\
% \makebox[6in]{\hrulefill}\\ 
%Professor Nevin Darwish, Thesis Main Advisor\\
% \makebox[6in]{\hrulefill}\\ 
%Professor Samia Mashali,Thesis Advisor \\
% \makebox[6in]{\hrulefill}\\  
%Assoc. Professor Magda Fayek,Thesis Advisor\\ 
% \makebox[6in]{\hrulefill}\\ 
%Professor  Ashraf Abd El Wahab, Member\\
% \makebox[6in]{\hrulefill}\\ 
%Professor Mohamed Zaki Abd ElMegeed, Member\\
% \makebox[6in]{\hrulefill}\\ 
  % \\   you need...\\
%\makeapproval                                           %

@@

                                                        % ACK. PAGE
                                                        %======================
\begin{acknowledgments}     
                            % Delete these if
All praise is due to Allah Who guided me to this. I could not truly have been led aright if Allah had not guided me.

@@

%------------------------------------------------------------------------------
%  Document body - Place text into individual include files, such as
%                  as "chap1.tex", or replace each "\include{}" statement
%                  with your actual document text.
%------------------------------------------------------------------------------
\begin{abstractpage}          
% ABSTRACT PAGE
%==============================
% Creates the abstract page.
%   Your text goes here. Just
%   follow the rules given in
%   the LaTeX manual on how to
%   enter/format text using
%   LaTeX commands.

@@

\end{abstractpage}                              % This ends the page.
